\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\title{Stem biology project forumla}
\author{Sirius Chan}
\begin{document}
\maketitle
\section*{Ingredients}
{
\centering
\begin{tabular}{|c|c|}
  \hline
  Item & Amount\\
  \hline
  \hline
  Distilled water & 300ml\\
  Agar & 3g\\
  Propionic acid & 1.2ml\\
  Methyl 4-hydroxybenzoate & 0.3g\\
  Ethanol & 1.3ml\\
  Brewers yeast & 15g\\
  Sucrose & 15g\\
  30ml vials & 20x\\
  \hline
\end{tabular}
\par
}

\section*{Method}
\begin{enumerate}
  \item Weigh out agar and place in 1 litre Simax reagent bottle.
  \item Add 200ml distilled water, leave cap loose and autoclave.
  \item Add propionic acid and methyl 4-$\dots$ in dissolved 1.3ml ethanol.
  \item Pour over sterile 30ml vials filling to approximately $\frac{1}{3}$ volume.
  \item In a different solution, dissolve 15g of yeast and 15g of sucrose in 100ml of distilled water.
  \item Prepare 2 more solutions, one of them being 15g of sucrose dissolved in 50ml of distilled water, and the other one being 15g of yeast dissolved in 50ml of water.
  \item Autoclave to sterilise the two solutions.
  \item Add 10ml of the solution containing agar to each vial. (Do I do this myself?)
  \item I'm going to add a different amount of the two solutions to each vial at this step. At this point, I will need 20 30ml vials each with 10ml of the solution containing agar, 50ml of yeast solution, 50ml of sucrose solution, and some amount of distilled water.
  \item Place all vials in a 55\textcelsius~water path to allow equilibriate.
  \item Cap vials and store in fridge, wait for it to set.
\end{enumerate}
\end{document}